Figures and tables for paper

### 2021-10-20 analysis/04_figs-tables.Rmd
Hypothesis 2b contrast plots, still need to write out answer

# Reference Level = Friendly relationship with government
#  contrasts <- tibble(
#    under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
#    criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
#    )

# Plot the contrasts
# contrasts %>%
#  pivot_longer(under_crackdown:criticized, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
# ggsave(
#  "contrasts_hypothesis02b.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
# )
```

>>>>

# Reference Level = Friendly relationship with government
intib <- interactions_2b %>% filter(i >= 14) %>% select(i, Gamma)

contrasts_int <- tibble(
  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = intib %>% filter(i == 17) %>% pull(),
  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty_criticized = oxfam_criticized - amnesty_criticized,
    oxfam_greenpeace_criticized = oxfam_criticized - greenpeace_criticized,
    red_cross_amnesty_criticized = red_cross_criticized - amnesty_criticized,
    red_cross_greenpeace_criticized = red_cross_criticized - greenpeace_criticized,
    oxfam_amnesty_crackdown = oxfam_crackdown - amnesty_crackdown,
    oxfam_greenpeace_crackdown = oxfam_crackdown - greenpeace_crackdown,
    red_cross_amnesty_crackdown = red_cross_crackdown - amnesty_crackdown,
    red_cross_greenpeace_crackdown = red_cross_crackdown - greenpeace_crackdown
  )
# Plot the contrasts
contrasts_int %>%
  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis02b.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
 )
```
